\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-06 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
** Fix process.sh and update README for examples/layered_halfspace ** Update manual: fix small formatting problems; add a note on 'decompose_mesh has to be run in bin/'

After the block definitions are done, you export the mesh using the
script \texttt{cubit2specfem3d.py} provided in each of the example
directories. If the export was successful, you should find the following
files in a subdirectory \texttt{MESH/}:
\begin{description}
\item [{absorbing\_cpml\_file}] \textbf{(only needed in case of C-PML absorbing
conditions)} Contains on the first line the total number of C-PML
spectral elements in the mesh, and then on the following line the
list of all these C-PML elements with two numbers per line: first
the spectral element number, and then a C-PML flag indicating to which
C-PML layer(s) that element belongs, according to the following convention:

@@

The partitioning is done in serial for now (in the next release we
will provide a parallel version of that code), the synopsis is: 
\begin{lyxcode}
./xdecompose\_mesh~nparts~input\_directory~output\_directory
\end{lyxcode}
where 
\begin{itemize}
\item \texttt{nparts} is the number of partitions, i.e., the number of cores
for the parallel simulations, 
\item \texttt{input\_directory} is the directory which holds all the files
generated by the Python script \texttt{cubit2specfem3d.py} explained
in the previous Section~\ref{subsec:Exporting-the-Mesh}, e.g. \texttt{MESH/},
and 
\item \texttt{output\_directory} is the directory for the output of this
partitioner which stores ACII-format files named like \texttt{proc{*}{*}{*}{*}{*}{*}\_Database}
for each partition. These files will be needed for creating the distributed
databases, and have to reside in the directory \texttt{LOCAL\_PATH}
specified in the main \texttt{Par\_file}, e.g. in directory \texttt{OUTPUT\_FILES/DATABASES\_MPI}.
Please see Chapter~\ref{cha:Creating-Distributed-Databases} for
further details. 
\end{itemize}
Note that all the files generated by the Python script \texttt{cubit2specfem3d.py}
must be placed in the \texttt{input\_directory} folder before running
the program.

@@

\begin{description}
\item [{\texttt{default}}] Uses model parameters as defined by meshing
procedures described in the previous Chapter~\ref{cha:Mesh-Generation}. 
\end{description}
\end{description}
\end{description}

\begin{description}
\item [{\textmd{1D~models~with~real~structure:}}] ~

\begin{description}
\item [{\texttt{1D\_prem}}] Isotropic version of the spherically symmetric
Preliminary Reference Earth Model (PREM) \citep{DzAn81}.

\begin{description}
\item [{\texttt{1D\_socal}}] A standard isotropic 1D model for Southern
California. 
\item [{\texttt{1D\_cascadia}}] Isotropic 1D profile for the Cascadia region. 
\end{description}
\end{description}
\end{description}

\begin{description}
\item [{\textmd{Fully~3D~models:}}] ~

@@

Adjoint simulations are generally performed for two distinct applications.
First, they can be used for earthquake source inversions, especially
earthquakes with large ruptures such as the Lander's earthquake \citep{WaHe94}.
Second, they can be used to generate finite-frequency sensitivity
kernels that are a critical part of tomographic inversions based upon
3D reference models \citep{TrTaLi05,LiTr06,TrKoLi08,LiTr08}. In either
case, source parameter or velocity structure updates are sought to
minimize a specific misfit function (e.g., waveform or traveltime
differences), and the adjoint simulation provides a means of computing
the gradient of the misfit function and further reducing it in successive
iterations. Applications and procedures pertaining to source studies
and finite-frequency kernels are discussed in Sections~\ref{sec:Adjoint-simulation-sources}
and \ref{sec:Adjoint-simulation-finite}, respectively. The two related
parameters in the \texttt{Par\_file} are \texttt{SIMULATION\_TYPE}
(1, 2 or 3) and the \texttt{SAVE\_FORWARD} (boolean).

@@

In the case where a specific misfit function is minimized to invert
for the earthquake source parameters, the gradient of the misfit function
with respect to these source parameters can be computed by placing
time-reversed seismograms at the receivers and using them as sources
in an adjoint simulation, and then the value of the gradient is obtained
from the adjoint seismograms recorded at the original earthquake location.
\begin{enumerate}
\item \textbf{Prepare the adjoint sources} \label{enu:Prepare-the-adjoint}

>>>>

After the block definitions are done, you export the mesh using the
script \texttt{cubit2specfem3d.py} provided in each of the example
directories (linked to the common script \texttt{CUBIT/cubit2specfem3d.py}). If the export was successful, you should find the following
files in a subdirectory \texttt{MESH/}:
\begin{description}
\item [{absorbing\_cpml\_file}] \textbf{(only needed in case of C-PML absorbing
conditions)} Contains on the first line the total number of C-PML
spectral elements in the mesh, and then on the following line the
list of all these C-PML elements with two numbers per line: first
the spectral element number, and then a C-PML flag indicating to which
C-PML layer(s) that element belongs, according to the following convention:

@@

The partitioning is done in serial for now (in the next release we
will provide a parallel version of that code). It needs to be run in the \texttt{bin/} directory because it expects the \texttt{../DATA/Par\_file}. The synopsis is: 
\begin{lyxcode}
./xdecompose\_mesh~nparts~input\_directory~output\_directory
\end{lyxcode}
where 
\begin{itemize}
\item \texttt{nparts} is the number of partitions, i.e., the number of cores
for the parallel simulations, 
\item \texttt{input\_directory} is the directory which holds all the files
generated by the Python script \texttt{cubit2specfem3d.py} explained
in the previous Section~\ref{subsec:Exporting-the-Mesh}, e.g. \texttt{MESH/},
and 
\item \texttt{output\_directory} is the directory for the output of this
partitioner which stores ACII-format files named like \texttt{proc{*}{*}{*}{*}{*}{*}\_Database}
for each partition. These files will be needed for creating the distributed
databases, and have to reside in the directory \texttt{LOCAL\_PATH}
specified in the main \texttt{Par\_file}, e.g. in directory \texttt{OUTPUT\_FILES/DATABASES\_MPI}.
Please see Chapter~\ref{cha:Creating-Distributed-Databases} for
further details. 
\end{itemize}
Note that all the files generated by the Python script \texttt{cubit2specfem3d.py}
must be placed in the \texttt{input\_directory} folder before running
the program.

@@

\begin{description}
\item [{\texttt{default}}] Uses model parameters as defined by meshing
procedures described in the previous Chapter~\ref{cha:Mesh-Generation}. 
\end{description}

\item [{\textmd{1D~models~with~real~structure:}}] ~

\begin{description}
\item [{\texttt{1D\_prem}}] Isotropic version of the spherically symmetric
Preliminary Reference Earth Model (PREM) \citep{DzAn81}. 
\item [{\texttt{1D\_socal}}] A standard isotropic 1D model for Southern
California. 
\item [{\texttt{1D\_cascadia}}] Isotropic 1D profile for the Cascadia region. 
\end{description}

\item [{\textmd{Fully~3D~models:}}] ~

@@

Adjoint simulations are generally performed for two distinct applications.
First, they can be used in point source moment-tensor inversions, or source imaging for
earthquakes with large ruptures such as the Lander's earthquake \citep{WaHe94}.
Second, they can be used to generate finite-frequency sensitivity
kernels that are a critical part of tomographic inversions based upon
3D reference models \citep{TrTaLi05,LiTr06,TrKoLi08,LiTr08}. In either
case, source parameter or velocity structure updates are sought to
minimize a specific misfit function (e.g., waveform or traveltime
differences), and the adjoint simulation provides a means of computing
the gradient of the misfit function and further reducing it in successive
iterations. Applications and procedures pertaining to source studies
and finite-frequency kernels are discussed in Sections~\ref{sec:Adjoint-simulation-sources}
and \ref{sec:Adjoint-simulation-finite}, respectively. The two related
parameters in the \texttt{Par\_file} are \texttt{SIMULATION\_TYPE}
(1, 2 or 3) and the \texttt{SAVE\_FORWARD} (boolean).

@@

When a specific misfit function between data and synthetics is minimized to invert
for earthquake source parameters, the gradient of the misfit function
with respect to these source parameters can be computed by placing
time-reversed seismograms at the receivers as virtual sources
in an adjoint simulation. Then the value of the gradient is obtained
from the adjoint seismograms recorded at the original earthquake location.
\begin{enumerate}
\item \textbf{Prepare the adjoint sources} \label{enu:Prepare-the-adjoint}
